Bayesian model comparison for rare variant association studies of multiple phenotypes

### 2018-01-30 tex/manuscript.tex
Updates

MRP allows users to specify priors that reflect knowledge of the variants and phenotypes under study. For instance, we can define an independent effects model where each variant in the model may have different effect sizes. In this case, $\mathbf{R_{\textrm{var}}}$ is the identity matrix which reflects the assumption that the effect sizes of the variants are not correlated. This could be true for missense variants where some variants may impact important functional domains but others do not. We can also define a similar effects model by setting every value of $\mathbf{R_{\textrm{var}}}$ to $\sim 1$. This model assumes that all variants under consideration have the same effect sizes. This model may be appropriate for PTVs where each variant completely disrupts the function of the gene, leading to a gene knockout. The prior on the scale of effect sizes can also be used to denote which variants may have larger effect sizes. For instance, emerging empirical genetic studies have shown that within a gene, PTVs may have stronger effects than missense variants\cite{do2015exome}. This can be reflected by providing larger priors for PTVs.

>>>>

MRP allows users to specify priors that reflect knowledge of the variants and phenotypes under study. For instance, we can define an independent effects model where each variant in the model may have different effect sizes. In this case, $\mathbf{R_{\textrm{var}}}$ is the identity matrix which reflects the assumption that the effect sizes of the variants are not correlated. We can also define a similar effects model by setting every value of $\mathbf{R_{\textrm{var}}}$ to $\sim 1$. This model assumes that all variants under consideration have similar effect sizes (with possibly differences in scale). This model may be appropriate for PTVs where each variant completely disrupts the function of the gene, leading to a gene knockout. The prior on the scale of effect sizes can also be used to denote which variants may have larger effect sizes. For instance, emerging empirical genetic studies have shown that within a gene, PTVs may have stronger effects than missense variants\cite{do2015exome}. This can be reflected by adjusting the prior spread of effect sizes ($\sigma$) for PTVs (\nameref{S1_Appendix}).
